\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}

\geometry{
    left=3cm,
    right=3cm,
}

\begin{document}

\title{Homework 1}
\author{Pupipat Singkhorn}
\date{\today}
\maketitle

\section*{Exercise 1}

\begin{enumerate}
    \item Describes the languages denoted by the following regular expressions:
    \begin{enumerate}
        \item $a(a|b)^*a$\\
        : All strings of `a' and `b' that starts and ends with `a'.
        \item $((\varepsilon|a)b^*)^*$\\
        : All strings of `a' and `b'.
        \item $(a|b)^*a(a|b)(a|b)$\\
        : All strings of `a' and `b' where the 3\textsuperscript{rd} element from the right is `a'.
        \item $a^*ba^*ba^*ba^*$\\
        : All strings of `a' and `b' that only contains three `b'.
        \item $(aa|bb)^*((ab|ba)(aa|bb)^*(ab|ba)(aa|bb)^*)^*$\\
        : All strings of `a' and `b' that has a even number of `a' and `b'.
    \end{enumerate}
    \item Write regular definitions for the following languages:
    \begin{enumerate}
        \item All strings of lowercase letters that contain the five vowels in order.
        \\ : other $\rightarrow$ [bcdfghjklmnpqrstvwxyz]
        \\ want $\rightarrow$ other*a(other$\mid$a)*e(other$\mid$e)*i(other$\mid$i)*o(other$\mid$o)*u(other$\mid$u)*
        \item All strings of lowercase letters in which the letters are in ascending lexicographic order.
        \\ : a* b* ... z*
        \item Comments, consisting of a string surrounded by \texttt{/*} and \texttt{*/}, without an intervening \texttt{*/}, unless it is inside double-quotes (\texttt{"}).
        \\ : 
        \item All strings of digits with no repeated digits. Hint: Try this problem first with a few digits, such as $\{0, 1, 2\}$.
        \\ : A $\rightarrow$ 0?2(02)*
        \\ want $\rightarrow$ 0$\mid$A?0?1(A0?1$\mid$01)*A?0?$\mid$A0?
        \item All strings of $a$'s and $b$'s that do not contain the substring $abb$.
        \\ : b*(a+b?)*
        \item All strings of $a$'s and $b$'s that do not contain the subsequence $abb$.
        \\ : b* $\mid$ b*a+ $\mid$ b*a+ba*
    \end{enumerate}
    \item Write character classes for the following sets of characters:
    \begin{enumerate}
        \item The first ten letters (up to "j") in either upper or lower case.
        \\ : [A-Ja-j]
        \item The lowercase consonants.
        \\ : [bcdfghjklmnpqrstvwxzy]
        \item The "digits" in a hexadecimal number (choose either upper or lower case for the "digits" above 9).
        \\ : [0-9a-f]
        \item The characters that can appear at the end of a legitimate English sentence (e.g., comma, exclamation point).
        \\ : [.?!]
    \end{enumerate}
    \item Design finite automata (deterministic or nondeterministic) for this language
    \begin{enumerate}
        \item All strings of digits with no repeated digits. Hint: Try this problem first with a few digits, such as $\{0, 1, 2\}$.
        \vfill
    \end{enumerate}
    \item Convert the following regular expressions to deterministic finite automata:
    \begin{enumerate}
        \item $(a|b)^*$
        \item $(a^*|b^*)^*$
        \item $((\varepsilon|a)|b^*)^*$
        \item $(a|b)^*abb(a|b)^*$
    \end{enumerate}
\end{enumerate}

\end{document}
